\documentclass[a4paper]{article}
\usepackage[english]{babel}
\usepackage{enumerate}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{amssymb}

\title{Work Diary}
\author{}
\date{15 October 2016}

\begin{document}
\maketitle
	

\section{Time and Work}

\subsection{Summary}
Didn't really have time to run Matlab codes yesterday, plus have to download and install Mac version of Matlab to my laptop so I can continue work over weekend!

Quite some read and writings and format correction, have to move the focus onto coding now!!
\begin{itemize}

	\item Run Matlab demos - bought personal licence for less than USD 200 (incl. Image Processing and Computer Vision toolbox) 
\end{itemize}

\subsection{Time and work breakdowns}
\begin{description}
	\item [10:10 - 11:17]:
	\begin{itemize}
		\item 10:10 - 10:30 
			\begin{itemize}
				\item Read supplementary materials, understand the IDS framework structure
				\item So basically two parts: Web service (i.e. TomCat) + ML (i.e. Matlab demo)
				\item Three methods in total:
					\begin{itemize}
						\item PCA
						\item LDA
						\item Proposed (PCA+LDA+ALO)
					\end{itemize}

				\item Four types of attacks:
					\begin{itemize}
						\item UDP
						\item ICMP
						\item TCP sync
						\item TCP PSH ACK
					\end{itemize}
			\end{itemize}
			
		\item 10:30 - 10:35
			\begin{itemize}
				\item First run of demo - works!! 
				\item this is great, I was really expecting some hard debugging times!
			\end{itemize}
		\item 10:35 - 11:40
			\begin{itemize}
				\item short distraction....
			\end{itemize}
		\item 10:40 - 11:00
			\begin{itemize}
				\item Now sort out the main process pipeline, use UDP + PCA as example
				\item Read input from 'udp\_Feat.mat'
				\item Directly call Matlab \textit{PCA} function
				\item 
			\end{itemize}
	\end{itemize}
	
	\item[15:15 - 16:15]:
	\begin{itemize}
		\item 15:15 - 15:20
			\begin{itemize}
				\item Downloaded 10 cloud computing papers from the client. Modified all file names so easier to refer in future.
				\item quickly identified 4 papers, simply by the title for quick reading.
				\item This is just the background reading. The goal is to understand the Computing Cloud concepts and more important how to write up properly for ML methods.
				\item Starts from two survey papers
			\end{itemize}
		\item 15:20 - 15:55
		\begin{itemize}
			\item Read first survey paper. Make notes.
			\item It's a good start, good concepts. Reading paper (and make the notes \& formats at the same time) is always time consuming though!!
		\end{itemize} 
		 
	\end{itemize}
\end{description}





%\begin{thebibliography}{99}
%
%\bibitem{thapngam2012ddos} Thapngam, Theerasak, Shui Yu, and Wanlei Zhou. "DDoS discrimination by linear discriminant analysis (LDA)." \textit{Computing, Networking and Communications (ICNC), 2012 International Conference on}. IEEE, 2012.
%
%\bibitem{aghdam2016feature} Aghdam, Mehdi Hosseinzadeh, and Peyman Kabiri. "Feature selection for intrusion detection system using ant colony optimization." \textit{International Journal of Network Security} 18.3 (2016): 420-432.
%
%\bibitem{fernandes2016network} Fernandes, Gilberto, et al. "Network anomaly detection using IP flows with Principal Component Analysis and Ant Colony Optimization." \textit{Journal of Network and Computer Applications} 64 (2016): 1-11.
%
%\end{thebibliography}

\end{document}


