\documentclass[a4paper]{article}
\usepackage[english]{babel}
\usepackage{enumerate}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{amssymb}

\title{Work Diary}
\author{}
\date{14 October 2016}

\begin{document}
\maketitle
	

\section{Time and Work}

\subsection{Summary}
Lunch time, plan to work about 2 hours on the project. Primarily reading. Will also test the Matlab codes for first time - that's the plan!
\begin{itemize}
	\item Background reading about cloud computing and network security papers that client has downloaded
	\item The original write-ups in the current version on ML algorithms is poor, very very poor. Plan to improve upon PCA, LDA and mainly focus on their differences to argue for the proposed method eventually
	\item Run Matlab demos if possible - bought personal licence for less than USD 200 (incl. Image Processing and Computer Vision toolbox) 
\end{itemize}

\subsection{Time and work breakdowns}
\begin{description}
	\item [12:15 - 13:18]:
	\begin{itemize}
		\item 12:15 - 12: 35
			\begin{itemize}
				\item PCA summary				
			\end{itemize}
		\item 12:35 - 12:53
			\begin{itemize}
				\item LDA summary
			\end{itemize}
		\item 12:55 - 13:13
			\begin{itemize}
				\item PCA adn LDA differences
			\end{itemize}
		\item 13:13 - 13:18
			\begin{itemize}
				\item Final touch to amend the wrong format e.g. typos, equations, etc.
				\item Sorting out the references used in the text
			\end{itemize}
	\end{itemize}
	
	\item[15:15 - 16:15]:
	\begin{itemize}
		\item 15:15 - 15:20
			\begin{itemize}
				\item Downloaded 10 cloud computing papers from the client. Modified all file names so easier to refer in future.
				\item quickly identified 4 papers, simply by the title for quick reading.
				\item This is just the background reading. The goal is to understand the Computing Cloud concepts and more important how to write up properly for ML methods.
				\item Starts from two survey papers
			\end{itemize}
		\item 15:20 - 15:55
		\begin{itemize}
			\item Read first survey paper. Make notes.
			\item It's a good start, good concepts. Reading paper (and make the notes \& formats at the same time) is always time consuming though!!
		\end{itemize} 
		 
	\end{itemize}
\end{description}





%\begin{thebibliography}{99}
%
%\bibitem{thapngam2012ddos} Thapngam, Theerasak, Shui Yu, and Wanlei Zhou. "DDoS discrimination by linear discriminant analysis (LDA)." \textit{Computing, Networking and Communications (ICNC), 2012 International Conference on}. IEEE, 2012.
%
%\bibitem{aghdam2016feature} Aghdam, Mehdi Hosseinzadeh, and Peyman Kabiri. "Feature selection for intrusion detection system using ant colony optimization." \textit{International Journal of Network Security} 18.3 (2016): 420-432.
%
%\bibitem{fernandes2016network} Fernandes, Gilberto, et al. "Network anomaly detection using IP flows with Principal Component Analysis and Ant Colony Optimization." \textit{Journal of Network and Computer Applications} 64 (2016): 1-11.
%
%\end{thebibliography}

\end{document}


